Fusion Moves for Correlation Clustering

### 2014-11-12 paper/egpaper_for_review.tex
fixed missing bracket in fast opt.

\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is still NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $y$ the original graph $G=(V,E)$ by
%
\begin{align}
y_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}
Furthermore, the back projection of the optimal segmentation $\bar{y}$ of the contracted graph is a solution of problem~\ref{eq:fusion_move_a}.

>>>>

\subsection{Fast Optimization of CCFusion Moves} \label{sec:fast_optimization}
In general the auxiliary fusion problem~\ref{eq:fusion_move_a} is still NP-hard.
However, many variables have been fixed to be zero and we can reformulate~\ref{eq:fusion_move_a}
into a correlation clustering problem on a coarser graph, where all nodes which are connected
via must-link constraints are merged into single nodes. We call this graph \emph{contracted graph}.
%
\begin{definition}\emph{(Contracted Graph)}
Given a weighted graph $G=(V,E,w)$ segmentation of $G$ given by $y\in P(G)$,
we denote by $S: V \to \mathbb{N}$ a mapping from the nodes to the segments.
We define the contraction of graph $G_y=(V_y,E_y, \bar{w})$
by $V_y=\{S(v)|v\in V\}$, $E_y=\{S(u)S(v)|uv\in E\}$, and 
$\forall \bar{u}\bar{v}\in E_y: \bar{w}_{\bar{u}\bar{v}}=\sum_{uv\in E, S(u)=\bar{u},S(v)=\bar{v}}w_{uv}$ 
\end{definition}
%
Any clustering $\bar{y}$ of the contracted graph $G_y=(V_y,E_y)$ can be \emph{back projected} to a clustering $y$ the original graph $G=(V,E)$ by
%
\begin{align}
y_{uv}&=\left\{ 
\begin{array}{ll}
\bar{y}_{S(u)S(v)}& \textrm{ if }S(u) \neq S(v)\\
0                & \textrm{ else}
\end{array}
\right.& \forall uv \in E
\end{align}
Furthermore, the back projection of the optimal segmentation $\bar{y}$ of the contracted graph is a solution of problem~\ref{eq:fusion_move_a}.
